---
title: "Regression Analyses"
author: "Jaewon Royce Choi"
date: "6/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

In this document, I will set up, run, and examine several multiple regression models. In general, the models aim to investigate the relationhips between **broadband** and **entrepreneurship**. Specifically, **how broadband influences entrepreneurship**. Furthermore, the models will explore how different measures of broadband, specifically measures of availability and adoption, explain entrepreneurial activities differently. Finally, I will explore how broadband as well as entrepreneurial factors contribute to the overall prosperity.

```{r Load packages & Get the dataset, results='hide'}

## Load packages
library(tidyverse)
library(ggplot2)
library(gridExtra)
#install.packages("stargazer", dependencies = T)    # A package for better looking tables for results
library(stargazer)

## Read in dataset
tx_bb_entrepreneur_merged_v2 <- read_csv("https://raw.githubusercontent.com/jwroycechoi/broadband-entrepreneurship/master/Datasets/Broadband-Entrepreneurship-TX-merged_v2.csv")

tx_bb_entrepreneur_merged_v2 <- tx_bb_entrepreneur_merged_v2 %>% 
  mutate(chg_pct_50_est_cbp_2012_2018 = pct_50_est_cbp_2018 - pct_50_est_cbp_2012,
         chg_pct_10_est_cbp_2012_2018 = pct_10_est_cbp_2018 - pct_10_est_cbp_2012,
         chgn_nonemp_2012_2018 = neest_nemp_2018 - neest_nemp_2012)

```

## Broadband and Entrepreneurship

First, let's take another look at some of the key variables.

> Entrepreneurship

* `IRR2010`: Rural index (larger = rural)
* `pct_change_pro_emp_2010_2017`: Change in % of sole proprietors b/w 2010-2017
* `chg_pct_10_est_cbp_2012_2018`: Change in % of establishments with less than 10 employees b/w 2012-2017
* `chg_pct_nonfarmneest_nemp_2012_2018`: Change in % of nonfarm nonemployer b/w 2012-2018
* `chgn_nonemp_2012_2018`: Change in nonemployer establishments b/w 2012-2018
* `pct_chg_bea_2012_2018`: Change in % of nonfarm proprietors b/w 2012-2018
* `venturedensity_mean`: Venture density
* `highlyactivevd_mean`: Highly active venture density

> Broadband

* `pct_broadband_FCC`: FCC broadband availability in % (2017)
* `pct_broadband_MS`: MS broadband availability in % (2019)
* `pct_fixed_acs_2018`: ACS broadband subscription in $ (2018)
* `pct_broadband_mlab`: M-Lab broadband measure (2019)

### Broadband's Effect on Entrepreneurial Outcome

Here I investigate **models that estimate broadband variables' effect on the entrepreneurial outcome.** Several different broadband measures are in the dataset. I will first model **each measure's relationship with the entrepreneurial outcome separately.**

Entrepreneurial outcomes can be represented by several variables in this dataset. As the ASU research team's white paper argued, the venture density provided by GoDaddy activities reflects actual entrepreneurial activities in the form of online domain creation. In the dataset, we also have Texas state's sole proprietor statistics. These variables reflect small and medium sized businesses in each county.

#### Control Variables

For control variables, various demographic measures derived from the ACS estimates are available in the dataset. Furthermore, the ruralithy of the counties are reflected in the IRR index. Number of population, and regional intustry characteristics will be also included as control variables.

## Change in Nonfarm Proprietors Share

* DV: Change in Nonfarm Proprietor Share (2012-2018)
* IV: FCC Broadband availability, MS Broadband, ACS Broadband Subscription, M-Lab Broadband Usage
* Control: Rurality, Industry structure, Education, Age

```{r Change in Nonfarm Proprietors Share, results='asis', echo=FALSE}
#### Model 1 ####

## DV: Change in Nonfarm Proprietors Share
## IV: Broadband Availability (FCC) -> MS -> ACS -> M-lab

model_nonfarm_1 <- lm(pct_chg_bea_2012_2018 ~ pct_broadband_FCC + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_nonfarm_2 <- lm(pct_chg_bea_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_nonfarm_3 <- lm(pct_chg_bea_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_nonfarm_4 <- lm(pct_chg_bea_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + pct_broadband_mlab + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_nonfarm_1, model_nonfarm_2, model_nonfarm_3, model_nonfarm_4, title = "Change in Nonfarm Proprietors Share Regression Results", type = "html",
          align = TRUE, dep.var.labels = c("Change in Nonfarm Proprietors Share"),
          covariate.labels = c("FCC Broadband Availability","MS Broadband","ACS Broadband Sub","M-Lab Broadband","Rurality Index (2010)","Agriculture","Construction","Wholesale","Retail","Transportation","IT","Finance","Professional","Education","Other occupation","Public","Highschool","College","Millenials","GenX","Babyboomer"), no.space = TRUE)

```

## Change in Establishment with <10 Employees (2012-2018)

* DV: Change in Establishment with <10 Employees (2012-2018)
* IV: FCC Broadband availability, MS Broadband, ACS Broadband Subscription, M-Lab Broadband Usage
* Control: Rurality, Industry structure, Education, Age

```{r Change in Establishment with <10 Employees, results='asis', echo=FALSE}
#### Model 2 ####

## DV: Change in Establishment with <10 Employees
## IV: Broadband Availability (FCC) -> MS -> ACS -> M-lab

model_10emp_1 <- lm(chg_pct_10_est_cbp_2012_2018 ~ pct_broadband_FCC + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_10emp_2 <- lm(chg_pct_10_est_cbp_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_10emp_3 <- lm(chg_pct_10_est_cbp_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_10emp_4 <- lm(chg_pct_10_est_cbp_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + pct_broadband_mlab + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_10emp_1, model_10emp_2, model_10emp_3, model_10emp_4, title = "Change in Establishment <10 Regression Results", type = "html",
          align = TRUE, dep.var.labels = c("Change in Establishment <10 Share"),
          covariate.labels = c("FCC Broadband Availability","MS Broadband","ACS Broadband Sub","M-Lab Broadband","Rurality Index (2010)","Agriculture","Construction","Wholesale","Retail","Transportation","IT","Finance","Professional","Education","Other occupation","Public","Highschool","College","Millenials","GenX","Babyboomer"), no.space = TRUE)
```

## Change in Nonfarm Nonemployers Share (2012-2018)

* DV: Change in Nonfarm Nonemployers Share (2012-2018)
* IV: FCC Broadband availability, MS Broadband, ACS Broadband Subscription, M-Lab Broadband Usage
* Control: Rurality, Industry structure, Education, Age

```{r Change in Nonfarm Nonemployers Share, results='asis', echo=FALSE}
#### Model 3 ####

## DV: Change in Nonfarm Nonemployers Share (2012-2018)
## IV: Broadband Availability (FCC) -> MS -> ACS -> M-lab

model_nf_nonemp_1 <- lm(chg_pct_nonfarmneest_nemp_2012_2018 ~ pct_broadband_FCC + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_nf_nonemp_2 <- lm(chg_pct_nonfarmneest_nemp_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_nf_nonemp_3 <- lm(chg_pct_nonfarmneest_nemp_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_nf_nonemp_4 <- lm(chg_pct_nonfarmneest_nemp_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + pct_broadband_mlab + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_nf_nonemp_1, model_nf_nonemp_2, model_nf_nonemp_3, model_nf_nonemp_4, title = "Change in Nonfarm Nonemployers Share Regression Results", type = "html",
          align = TRUE, dep.var.labels = c("Change in Nonfarm Nonemployers Share"),
          covariate.labels = c("FCC Broadband Availability","MS Broadband","ACS Broadband Sub","M-Lab Broadband","Rurality Index (2010)","Agriculture","Construction","Wholesale","Retail","Transportation","IT","Finance","Professional","Education","Other occupation","Public","Highschool","College","Millenials","GenX","Babyboomer"), no.space = TRUE)

```

## Change in Nonemployer Establishments (2012-2018)

* DV: Change in Nonemployer Establishments (2012-2018)
* IV: FCC Broadband availability, MS Broadband, ACS Broadband Subscription, M-Lab Broadband Usage
* Control: Rurality, Industry structure, Education, Age

```{r Change in nonemployer establishments 2012-2018, results='asis', echo=FALSE}
#### Model 4 ####

## DV: Change in Nonemployer Establishments (2012-2018)
## IV: Broadband Availability (FCC) -> MS -> ACS -> M-lab

model_nonemp_1 <- lm(chgn_nonemp_2012_2018 ~ pct_broadband_FCC + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_nonemp_2 <- lm(chgn_nonemp_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_nonemp_3 <- lm(chgn_nonemp_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_nonemp_4 <- lm(chgn_nonemp_2012_2018 ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + pct_broadband_mlab + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_nonemp_1, model_nonemp_2, model_nonemp_3, model_nonemp_4, title = "Change in Nonemployer Regression Results", type = "html",
          align = TRUE, dep.var.labels = c("Change in Nonemployer"),
          covariate.labels = c("FCC Broadband Availability","MS Broadband","ACS Broadband Sub","M-Lab Broadband","Rurality Index (2010)","Agriculture","Construction","Wholesale","Retail","Transportation","IT","Finance","Professional","Education","Other occupation","Public","Highschool","College","Millenials","GenX","Babyboomer"), no.space = TRUE)
```

## Venture Density

* DV: Venture Density
* IV: FCC Broadband availability, MS Broadband, ACS Broadband Subscription, M-Lab Broadband Usage
* Control: Rurality, Industry structure, Education, Age

```{r Venture Density, results='asis', echo=FALSE}
#### Model 4 ####

## DV: Venture density
## IV: Broadband Availability (FCC) -> MS -> ACS -> M-lab

model_vd_1 <- lm(venturedensity_mean ~ pct_broadband_FCC + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_2 <- lm(venturedensity_mean ~ pct_broadband_FCC + pct_broadband_MS + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_3 <- lm(venturedensity_mean ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_4 <- lm(venturedensity_mean ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + pct_broadband_mlab + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_vd_1, model_vd_2, model_vd_3, model_vd_4, title = "Venture Density Regression Results", type = "html",
          align = TRUE, dep.var.labels = c("Venture Density"),
          covariate.labels = c("FCC Broadband Availability","MS Broadband","ACS Broadband Sub","M-Lab Broadband","Rurality Index (2010)","Agriculture","Construction","Wholesale","Retail","Transportation","IT","Finance","Professional","Education","Other occupation","Public","Highschool","College","Millenials","GenX","Babyboomer"), no.space = TRUE)

```

## Highly Active Venture Density

* DV: Highly Active Venture Density
* IV: FCC Broadband availability, MS Broadband, ACS Broadband Subscription, M-Lab Broadband Usage
* Control: Rurality, Industry structure, Education, Age

```{r Highly Active Venture Density, results='asis', echo=FALSE}
#### Model 4 ####

## DV: Highly Active Venture density
## IV: Broadband Availability (FCC) -> MS -> ACS -> M-lab

model_havd_1 <- lm(highlyactive_vd_mean ~ pct_broadband_FCC + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_havd_2 <- lm(highlyactive_vd_mean ~ pct_broadband_FCC + pct_broadband_MS + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_havd_3 <- lm(highlyactive_vd_mean ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_havd_4 <- lm(highlyactive_vd_mean ~ pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + pct_broadband_mlab + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_havd_1, model_havd_2, model_havd_3, model_havd_4, title = "Highly Active Venture Density Regression Results", type = "html",
          align = TRUE, dep.var.labels = c("Highly Active Venture Density"),
          covariate.labels = c("FCC Broadband Availability","MS Broadband","ACS Broadband Sub","M-Lab Broadband","Rurality Index (2010)","Agriculture","Construction","Wholesale","Retail","Transportation","IT","Finance","Professional","Education","Other occupation","Public","Highschool","College","Millenials","GenX","Babyboomer"), no.space = TRUE)

```


### Models with Proprietor/Nonemp as IV

Below, I explore regression models that consider **proprietors share or nonemployer establishments as independent variables** representing overall industry characteristics of the county. Dependent variables are **venture density** measures as representations of entrepreneurial activities online.

* DV: Venture Density, Highly Active Venture Density
* IV: Nonfarm Proprietor Share, Nonemployer, FCC Broadband availability, MS, ACS, M-Lab
* Control: Rurality, Education, Age

```{r Venture Density and Proprietor as IV, results='asis', echo=FALSE}

model_vd_2.1 <- lm(venturedensity_mean ~ pct_nonfarm_bea_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_2.2 <- lm(venturedensity_mean ~ pct_nonfarm_bea_2018 + nonfarmneest_nemp_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_2.3 <- lm(venturedensity_mean ~ pct_nonfarm_bea_2018 + nonfarmneest_nemp_2018 + pct_broadband_FCC + pct_broadband_MS + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_2.4 <- lm(venturedensity_mean ~ pct_nonfarm_bea_2018 + nonfarmneest_nemp_2018 + pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + pct_broadband_mlab + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_vd_2.1, model_vd_2.2, model_vd_2.3, model_vd_2.4, type = "html", align = T,
          dep.var.labels = c("Venture Density"),
          covariate.labels = c("Nonfarm Proprietor (%)",
                               "Nonfarm Nonemployer",
                               "FCC Broadband Availability",
                               "MS Broadband",
                               "ACS Broadband Subs",
                               "M-Lab Broadband Use",
                               "Rurality Index (2010)",
                               "Agriculture",
                               "Construction",
                               "Wholesale",
                               "Retail",
                               "Transportation",
                               "IT",
                               "Finance",
                               "Professional",
                               "Education",
                               "Other occupation","Public","Highschool","College","Millenials","GenX","Babyboomer"),
          no.space = T)


```

## MS Broadband Availability

* DV: Venture Density, Highly Active VD, Change in Nonfarm Proprietor Share (2012-2018)
* IV: MS Broadband 
* Control: Rurality, Education, Age

```{r Highly Active VD and Proprietor as IV, results='asis', echo=FALSE}

model_havd_2.1 <- lm(highlyactive_vd_mean ~ pct_nonfarm_bea_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_havd_2.2 <- lm(highlyactive_vd_mean ~ pct_nonfarm_bea_2018 + nonfarmneest_nemp_2018 + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_havd_2.3 <- lm(highlyactive_vd_mean ~ pct_nonfarm_bea_2018 + nonfarmneest_nemp_2018 + pct_broadband_FCC + pct_broadband_MS + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

model_havd_2.4 <- lm(highlyactive_vd_mean ~ pct_nonfarm_bea_2018 + nonfarmneest_nemp_2018 + pct_broadband_FCC + pct_broadband_MS + pct_fixed_acs_2018 + pct_broadband_mlab + IRR2010 + pctagriculture + pctconstruction + pctwholesale + pctretail + pcttransportation + pctinformation_tech + pctfinance + pctprofessional + pcteducation + pctother_occupation + pctpublic + pcthighschool + pctcollege + pctmillennial + pctgenx + pctbabyboomer,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_havd_2.1, model_havd_2.2, model_havd_2.3, model_havd_2.4, type = "html", align = T,
          dep.var.labels = c("Highly Active Venture Density"),
          covariate.labels = c("Nonfarm Proprietor (%)",
                               "Nonfarm Nonemployer",
                               "FCC Broadband Availability",
                               "MS Broadband",
                               "ACS Broadband Subs",
                               "M-Lab Broadband Use",
                               "Rurality Index (2010)",
                               "Agriculture",
                               "Construction",
                               "Wholesale",
                               "Retail",
                               "Transportation",
                               "IT",
                               "Finance",
                               "Professional",
                               "Education",
                               "Other occupation","Public","Highschool","College","Millenials","GenX","Babyboomer"),
          no.space = T)

```



